### 2020-09-12 code/figure1.Rmd
Fix fig1 heatmap clip off, fix fig2 metastasis color annotation, add url to shinyapp in manuscript and supplemental_methods

fig1 <- ggplot(data = cancer_disrupt_heatmap, aes(x=sample_id, y=path_name, fill = membership)) + 
  geom_tile(size = 0.6) +
  scale_fill_manual(values = c("grey", "firebrick3"),
                    labels = c("Not Mutated", "Mutated")) +
  facet_grid(.~type, scales = "free", space = "free", switch = "x") + ## facet by cancer type; switch: move facet labels top to bottom
  xlab("") + ylab("377 Reactome Pathways") + labs(fill = "") +
  guides(fill = guide_legend(override.aes = list(size = 2))) + ## make fill legend shape smaller
  theme(axis.text.x = element_blank(), ## turn off x axis text
        axis.text.y = element_blank(), ## turn off y axis text
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(), ## remove tick marks
        strip.text.x = element_text(angle = 90), ## rotate x-axis
        strip.background = element_blank(),
        legend.position = "bottom", ## legend parameters
        legend.key.height = unit(1, "lines"),
        legend.text = element_text(size = 8),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,0,-10),
        plot.margin = unit(c(0.6, -3, 0, 0), "cm"),
        panel.background = element_rect(fill = "transparent"))

>>>>

fig1 <- ggplot(data = cancer_disrupt_heatmap, aes(x=sample_id, y=path_name, fill = membership)) + 
  geom_tile(size = 0.6) +
  scale_fill_manual(values = c("grey", "firebrick3"),
                    labels = c("Not Mutated", "Mutated")) +
  facet_grid(.~type, scales = "free", space = "free", switch = "x") + ## facet by cancer type; switch: move facet labels top to bottom
  xlab("") + ylab("377 Reactome Pathways") + labs(fill = "") +
  guides(fill = guide_legend(override.aes = list(size = 2))) + ## make fill legend shape smaller
  theme(axis.text.x = element_blank(), ## turn off x axis text
        axis.text.y = element_blank(), ## turn off y axis text
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(), ## remove tick marks
        strip.text.x = element_text(angle = 90), ## rotate x-axis
        strip.background = element_blank(),
        legend.position = "bottom", ## legend parameters
        legend.key.height = unit(1, "lines"),
        legend.text = element_text(size = 8),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,0,-10),
        plot.margin = unit(c(0.6, 0, 0, 0), "cm"),
        panel.background = element_rect(fill = "transparent"))

### 2020-09-12 code/figure2.Rmd
Fix fig1 heatmap clip off, fix fig2 metastasis color annotation, add url to shinyapp in manuscript and supplemental_methods

with(brca_subtype,
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = B_color, pch = 21, cex = 0.8, lwd = 0.2, 
               theta = 0, phi = 65, scale = F,
               xlim = c(-6, 4.5), zlim = c(-4.5, 4), ylim = c(-4, 5),
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(B_color[1:2]), col=B_color[1:2], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.07), legend=names(B_color[3:4]), col=B_color[3:4], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.14), legend=names(B_color[5:6]), col=B_color[5:6], pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("B", side=3, line=-1.2, cex=1, adj=0)

@@

C_colors <- c('#33a02c', '#e31a1c', '#ff7f00') ## Color scheme 
names(C_colors) <- c("BRCA1", "BRCA2", "BRCA1,BRCA2") ## Assigning mutation type to color
with(brca %>% filter(mut_type != "NA"), ## Filter samples that do not have a mutation in BRCA1 or BRCA2
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = C_colors, pch = 21, cex = 0.8, lwd = 0.2,
               theta = 0, phi = 65, scale = F,
               xlim = c(-6, 4.5), zlim = c(-4.5, 4), ylim = c(-4, 5),
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(C_colors[c(1:2)]), col=C_colors[c(1:2)], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.07), legend=names(C_colors[c(3)]), col=C_colors[3], pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("C", side=3, line=-1.2, cex=1, adj=0)

@@

D_colors <- c('darkgoldenrod3','dodgerblue3','yellow3','tomato2') ## Color scheme
names(D_colors) <- c("Stage I", "Stage II", "Stage III", "Stage IV") ## Assign stage to color
with(umap_cancertype %>% filter(ajcc_pathologic_tumor_stage != "Not Available"), ## Filter samples that do not have stage info
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = D_colors, pch = 21, cex = 0.8, lwd = 0.2,
               theta = 0, phi = 65, scale = F,
               xlim = c(-6, 4.5), zlim = c(-4.5, 4), ylim = c(-4, 5),
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(D_colors[1:2]), col=D_colors[1:2], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.07), legend=names(D_colors[3:4]), col=D_colors[3:4], pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("D", side=3, line=-1.2, cex=1, adj=0)

@@

E_colors <- c('#a6cee3','#1f78b4') ## Color scheme
names(E_colors) <- c("M0", "M1") ## Assign metastasis to color
with(umap_cancertype %>% filter(ajcc_metastasis_pathologic_pm %in% c("M0", "M1")), ## Only M0 and M1 tumor samples
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = E_colors, pch = 21, cex = 0.8, lwd = 0.2,
               theta = 0, phi = 65, scale = F,
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(E_colors), col=E_colors, pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("E", side=3, line=-1.2, cex=1, adj=0)

>>>>

with(brca_subtype,
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = B_color[as.character(Subtype_Selected)], pch = 21, cex = 0.8, lwd = 0.2, 
               theta = 0, phi = 65, scale = F,
               xlim = c(-6, 4.5), zlim = c(-4.5, 4), ylim = c(-4, 5),
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(B_color[1:2]), col=B_color[1:2], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.07), legend=names(B_color[3:4]), col=B_color[3:4], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.14), legend=names(B_color[5:6]), col=B_color[5:6], pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("B", side=3, line=-1.2, cex=1, adj=0)

@@

C_colors <- c('#33a02c', '#e31a1c', '#ff7f00') ## Color scheme 
names(C_colors) <- c("BRCA1", "BRCA2", "BRCA1,BRCA2") ## Assigning mutation type to color
with(brca %>% filter(mut_type != "NA"), ## Filter samples that do not have a mutation in BRCA1 or BRCA2
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = C_colors[as.character(mut_type)], pch = 21, cex = 0.8, lwd = 0.2,
               theta = 0, phi = 65, scale = F,
               xlim = c(-6, 4.5), zlim = c(-4.5, 4), ylim = c(-4, 5),
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(C_colors[c(1:2)]), col=C_colors[c(1:2)], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.07), legend=names(C_colors[c(3)]), col=C_colors[3], pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("C", side=3, line=-1.2, cex=1, adj=0)

@@

D_colors <- c('darkgoldenrod3','dodgerblue3','yellow3','tomato2') ## Color scheme
names(D_colors) <- c("Stage I", "Stage II", "Stage III", "Stage IV") ## Assign stage to color
with(umap_cancertype %>% filter(ajcc_pathologic_tumor_stage != "Not Available"), ## Filter samples that do not have stage info
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = D_colors[as.character(ajcc_pathologic_tumor_stage)], pch = 21, cex = 0.8, lwd = 0.2,
               theta = 0, phi = 65, scale = F,
               xlim = c(-6, 4.5), zlim = c(-4.5, 4), ylim = c(-4, 5),
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(D_colors[1:2]), col=D_colors[1:2], pch = 20, bty = "n", horiz = T, cex = 0.8)
legend("top", inset = c(0.07), legend=names(D_colors[3:4]), col=D_colors[3:4], pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("D", side=3, line=-1.2, cex=1, adj=0)

@@

E_colors <- c('#a6cee3','#1f78b4') ## Color scheme
names(E_colors) <- c("M0", "M1") ## Assign metastasis to color
with(umap_cancertype %>% filter(ajcc_metastasis_pathologic_pm %in% c("M0", "M1")), ## Only M0 and M1 tumor samples
     scatter3D(plot_y, -plot_z, plot_x, 
               bg = E_colors[as.character(ajcc_metastasis_pathologic_pm)], pch = 21, cex = 0.8, lwd = 0.2,
               theta = 0, phi = 65, scale = F,
               xlab = "", ylab = "UMAP 3", zlab = "UMAP 1",
               colvar = NULL))
## Axis labels
legend("top", inset = c(0), legend=names(E_colors), col=E_colors, pch = 20, bty = "n", horiz = T, cex = 0.8)
title(xlab="UMAP 2", line=-0.25)
mtext("E", side=3, line=-1.2, cex=1, adj=0)
